European or American? A re-examination of the transatlantic influence over the IMF

### 2025-07-12 manuscript/manuscript.qmd
Bugfix: read RDS data rather than dta
add europe-disaggregated table

```{r}
#| label: fig-data
dta <- haven::read_dta('data/panel_data.dta')
```

@@

>>>>

```{r}
#| label: fig-data
dta <- readr::read_rds('data/panel_data.rds')
```

@@

```{r}
#| label: tbl-results-europe
#| tbl-cap: Effects of U.S. and European Influence on IMF Lending Outcomes (1980–2010), Separating European and Non-European Recipients
#| tbl-pos: H
load('save/regTable_europe.RData')
resultsTable |> tinytable::theme_tt("resize", width = 1)
```
